The CMS Data Aggregation System

### 2010-05-04 doc/das_paper/paper.tex
More update on Future work section
git-svn-id: svn+ssh://svn.cern.ch/reps/CMSDMWM/DAS/trunk@982 4525493e-7705-40b1-a816-d608a930855b

\section{Future work}
The DAS system was desgined for CMS HEP experiment, while its architecture is
transparent to participating data-providers and stored meta-data. 
In the near future we plan to put DAS into production and confirm its scalability, 
transparency and durability for various CMS data-services. Our goal is to sustain 
1TB of meta-data per year. In long term, we would like to use DAS across various
data-services in HEP community and other disciplines. Such work has began under 
umbrella of DISCOVER Research Service Group at Cornell University \cite{DRSG} 
who expressed their interest to use DAS in other scientific domains.

>>>>

\section{Future work}
In the near future we plan to put DAS into production and confirm its scalability, 
transparency and durability for various CMS data-services. 
Our interests are plug-able interface for participating data-providers;
analytics framework and pre-fetch strategies as well as horizontal scaling of the
system. Our goal is to sustain 1TB of meta-data per year. 
In a long term, we would like to use DAS across various
data-services in HEP community and other disciplines. Even though the DAS was developed
for CMS HEP experiment, its architecture is transparent to participating 
data-providers and meta-data content. Therefore the generalization of DAS is feasible.
Such work has began under the umbrella of DISCOVER Research Service Group at 
Cornell University \cite{DRSG} who expressed their interest to use DAS in other 
scientific domains.
